---
title: "👋 Hi, I'm Carlos Austin!"
---

## About Me

I'm currently sharpening my data skills as a master's candidate at Baruch College, majoring in business analytics with a concentration in data analytics. My professional journey began as a researcher at MDRC, where I studied the impact of policies and programs on people with low incomes. This role ignited my passion for using data to drive positive change. I am now continuing my journey in data at the MTA, where I analyze AI-powered camera enforcement systems and their impact on bus operations and transportation efficiency.

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -74.0130
baruch_latitude  <- +40.7045

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am an employee at the <b>MTA</b>!")
```

## 🛠️ Skills

- **SQL**
- **Excel** 
- **Python** 
- **Tableau**
- **Power BI**
- Data Cleaning & Analysis
- Research & Impact Evaluation
- Causal Inference and Randomized Controlled Trials

## 📌 Notable Experience

**MTA**  
*Data Analyst* 

- Evaluate performance of AI-powered camera enforcement systems
- Query and analyze large-scale traffic enforcement data using SQL and Python, leveraging ArcGIS for spatial analysis to identify violation patterns and geographic hotspots across New York City
- Develop interactive dashboards and visualizations in Power BI to support operational decision-making and program evaluation



**MDRC**  
*Researcher* 

- Studied how policies and programs affect people with low incomes  
- Developed expertise in data-driven evaluation and impact analysis

---

## 🎓 Education

- **Baruch College** — MS, Business Analytics (Data Analytics)
- **New York University (NYU)** — BA, Politics

---

## 🌍 Interests

- Sports & Fitness
- Playing the Guitar
- Traveling

---

## 💬 Favorite Quote

> "Our deepest fear is not that we are inadequate. Our deepest fear is that we are powerful beyond measure. It is our light, not our darkness that most frightens us. We ask ourselves, 'Who am I to be brilliant, gorgeous, talented, fabulous?' Actually, who are you not to be? You are a child of God."

---

## 🔗 Connect with Me

[![LinkedIn](https://img.shields.io/badge/LinkedIn-blue?logo=linkedin&logoColor=white)](https://www.linkedin.com/in/carlos-austin-ba4598187/)  
📧 carlos.k.austin@gmail.com

---

_Thanks for visiting my profile! Let's connect and grow together in the world of data!_

```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`